---
title: "Analysis"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyr)
library(dplyr)
library(igraph)
library(DescTools)
library(GGally)
library(ggplot2)
library(datawizard)
library(DirectedClustering)
library(intergraph)
library(data.table)
library(xtable)
library(ggpubr)
library(rempsyc)
library(schoRsch)
library(kableExtra)
library(ggpmisc)
library(broom)
```

# Create Network objects
```{r}
## Create graphs

totsubs_list <- list("socialism","LateStageCapitalism","SandersForPresident","antiwork","democrats","Conservative","Libertarian","The_Mueller","neoliberal","Republican","Foodforthought","geopolitics","moderatepolitics","PoliticalDiscussion","politics", "MonsterHunter","chelseafc","GlobalOffensive","ShingekiNoKyojin","XboxSeriesX","Accounting","woodworking","okbuddychicanery","LosAngeles","gadgets","realhousewives","travel","Watches","MechanicAdvice","Amd")

# Create Directed graphs from the csv files obtained in "NetworkDataProcessing.Rmd".
for(sub in totsubs_list) {
  edges <- read.csv(paste("Edges_",sub,".csv",sep=""))
  nodes <- read.csv(paste("Nodes_",sub,".csv",sep=""))
  assign(paste0("g_", sub), graph_from_data_frame(edges, directed=T, vertices = nodes))
}

## Create undirected graphs

for(sub in totsubs_list) {
  edges <- read.csv(paste("Edges_",sub,".csv",sep=""))
  nodes <- read.csv(paste("Nodes_",sub,".csv",sep=""))
  assign(paste("g_", sub,"_ud",sep=""), graph_from_data_frame(edges, directed=F, vertices = nodes))
}

```

# Functions 
```{r}
# Gini coefficient
Gini_sub <- function(subreddit) {

fulldata <- read.csv(subreddit)

countcomms <- tally(group_by(fulldata, author))

# exclude authors with less than 5 comments (as in network)
cc4 <- countcomms[countcomms$n > 4,]

Gini(cc4$n, unbiased=F)
}


# Reciprocity 

rho_calc <- function(g){

# Garlaschelli and loffredo definition
r <- igraph::reciprocity(g)
a <- ecount(g)/(vcount(g)*(vcount(g)-1))
rho <- (r-a)/(1-a)
return(rho)

}

# Rescale (for ease of use later, to rescale from 0 to 1 rather than from 0 to 100)
RS <- function(x){
  rescale(x, to=c(0,1))
}

```

# Indicators 

## Gini coefficient
```{r}
Sublist <- list()
GiniCoefficient <- list()

# Gini coefficient for each subreddit
for (sub in totsubs_list) {
  Sublist <- append(Sublist, sub)
  GiniCoefficient <- append(GiniCoefficient, Gini_sub(paste(sub,".csv",sep="")))
}

# Create Dataframe 
df_ind <- data.frame(Subreddit=unlist(Sublist), Gini=unlist(GiniCoefficient))
```

## Reciprocity

```{r}
# reciprocity for each subreddit
rec <- list()
for (sub in totsubs_list) {
  rec <- append(rec, rho_calc(eval(parse(text=paste("g_",sub,sep="")))))
}

df_ind$Reciprocity<- unlist(rec)


```

## Degree Centrality

```{r}
# degree centrality for each subreddit
deg <- list()
for (sub in totsubs_list) {
  deg <- append(deg, mean(degree(eval(parse(text=paste("g_",sub,sep=""))))))
}
df_ind$Degree <- unlist(deg)

```

## Clustering

```{r}
# Global Clustering Coefficient (transitivity) for each subreddit
cluster <- list()
for (sub in totsubs_list) {
  cluster <- append(cluster, transitivity(type="global", eval(parse(text=paste("g_",sub,"_ud",sep="")))))
}
df_ind$Cluster <- unlist(cluster)

df_ind$Cluster_sq <- sqrt(df_ind$Cluster)

# Remove original Cluster measure
df_ind <- subset(df_ind, select=-(Cluster))

```

## Size (check)
```{r}
# Size for each subreddit (robustness check 1 (4.2.3.))
size <- list()
for (sub in totsubs_list) {
  size<- append(size, length(eval(parse(text=paste("g_",sub,sep="")))))
}

df_ind$Size <- unlist(size)

```

## Summary Table B.1

```{r}
rnd3 <- function(x){
  round(x,digits=3)
}

dftab <- data.frame(psych::describe(df_ind))
dftab <- dftab[-c(1,6),]

rownames(dftab) <- c("Gini","Reciprocity","Degree","Clustering Coefficient (Sqrt)")

dftab <- subset(dftab, select=c(3,4,5,8,9,11))

colnames(dftab) <- c("Mean", "SD", "Median", "Min", "Max", "Skew")

dftab[1:6] <- lapply(dftab[1:6], rnd3)

kable(dftab, booktabs=T,linesep="", format="latex", caption="Indicators, Descriptive Statistics") %>%
kable_styling(position="center", full_width = F)# %>% save_kable("TableDesc1.tex") 

```

## Indicator Statistics

```{r}
summary(df_ind$Reciprocity)
sd(df_ind$Reciprocity)
df_ind[which.min(df_ind$Reciprocity),]
df_ind[which.max(df_ind$Reciprocity),]

summary(df_ind$Cluster_sq)
sd(df_ind$Cluster_sq)
df_ind[which.min(df_ind$Cluster_sq),]
df_ind[which.max(df_ind$Cluster_sq),]

df_ind$Cluster <- unlist(cluster)
summary(df_ind$Cluster)
sd(df_ind$Cluster)
df_ind[which.min(df_ind$Cluster),]
df_ind[which.max(df_ind$Cluster),]
df_ind <- subset(df_ind, select=-(Cluster))

summary(df_ind$Degree)
sd(df_ind$Degree)
df_ind[which.min(df_ind$Degree),]
df_ind[which.max(df_ind$Degree),]

summary(df_ind$Gini)
sd(df_ind$Gini)
df_ind[which.min(df_ind$Gini),]
df_ind[which.max(df_ind$Gini),]

```



### Size Distribution

```{r}
# approx optimal bandwidth

iqr_size <- IQR(df_ind$Size)

binwidth <- 2 * iqr_size / (length(df_ind$Size)^(1/3))
ggplot(df_ind, aes(x=Size)) + geom_histogram(binwidth = 2000, color="#FFFFFF", fill="#4c72b0") + geom_vline(xintercept = mean(df_ind$Size), color="#002147", linetype="dashed", linewidth=0.8)+
  annotate("text", x=(mean(df_ind$Size)+400 ), y=12, label=paste("Mean =", round(mean(df_ind$Size),3)), 
           color="#002147", size=4.5, vjust=1, hjust=0) + 
    geom_vline(xintercept = median(df_ind$Size), color="blue", linetype="dashed", linewidth=0.8) +  annotate("text", x=(median(df_ind$Size)-5100), y=12, label=paste("Median =", round(median(df_ind$Size),3)), 
           color="blue", size=4.5, vjust=1, hjust=0) 

df_ind[which.min(df_ind$Size),]



```


# Figure 3 (Pairwise Correlation)

```{r}

lowerFn <- function(data, mapping, method = "lm", method2="lm", ...) {
  p <- ggplot(data = data, mapping = mapping) +
    geom_point(colour = "black") +
    geom_smooth(method = method, color = "red",fill="red", ...)+
    geom_smooth(method= method2, color="blue",fill="blue",...) +     stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")),
                 formula = y ~ x,
                 label.x.npc = "left", label.y.npc = 0.99,
                 parse = TRUE)
  p
}
dfcp <- df_ind
names(dfcp)[5] <- "Clustering \nCoefficient(sqrt)"

#tiff("indcorplot1.tiff", units="in", width=8, height=5, res=300)
g <-  ggpairs(dfcp, columns = c(2:(ncol(dfcp)-1)), lower = list(continuous = wrap(lowerFn, method = "loess",method2="lm"))) + theme_bw() + 
  theme(strip.text.y = element_text(size = 8))
g

#dev.off()

#g2 <-  ggpairs(df_rs, columns = c(2:ncol(df_rs)), lower = list(continuous = wrap(lowerFn, method = "loess",method2="lm")))
#g2
```


# Rescale and Create Index

```{r}
df_ind$Size <- as.numeric(df_ind$Size)

df_rs
df_rs$Gini <- as.numeric(RS(df_rs$Gini))
df_rs$Reciprocity <- as.numeric(RS(df_rs$Reciprocity))
df_rs$Degree <- as.numeric(RS(df_rs$Degree))
df_rs$Cluster_sq <- as.numeric(RS(df_rs$Cluster_sq))
df_rs$Size <- as.numeric(RS(df_rs$Size))


df_rs$EC_Index <- (df_rs$Gini + df_rs$Reciprocity + df_rs$Degree + df_rs$Cluster_sq) /4



summary(df_rs$EC_Index)

#tiff("indcorplot2.tiff", units="in", width=8, height=5, res=300)


#g2 <-  ggpairs(df_rs, columns = c(2:5,7), lower = list(continuous = wrap(lowerFn, method = "loess",method2="lm")))
#g2

#dev.off()


df_rs[which.max(df_rs$EC_Index),]
df_rs[which.min(df_rs$EC_Index),]



```

## Code type and ideology

```{r}
df_rs$type <- c("P","P","P","P","P","P","P","P","P","P","P","P","P","P","P","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP")

df_rs$ideology <- c("L","L","L","L","L","R","R","R","R","R","N","N","N","N","N","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP","NP")

```


## Divide into parwise comparisons
```{r}
df_L_R <- df_rs[df_rs$ideology=="L" | df_rs$ideology=="R",]

df_L_NP <- df_rs[df_rs$ideology=="L" | df_rs$ideology=="NP",]

df_L_N <- df_rs[df_rs$ideology=="L" | df_rs$ideology=="N",]

df_N_NP <- df_rs[df_rs$ideology=="N" | df_rs$ideology=="NP",]

df_N_R <- df_rs[df_rs$ideology=="N" | df_rs$ideology=="R",]

df_NP_R <- df_rs[df_rs$ideology=="NP" | df_rs$ideology=="R",]


```

## Table 1

```{r}

sub_indices <- df_rs[,c("EC_Index", "Reciprocity","Gini","Degree","Cluster_sq")]

sub_indices
colnames(sub_indices) <- c("Echo Chamber Index","Reciprocity","Gini","Degree","Clustering \nCoefficient (Square Root)")

dftab2 <- data.frame(psych::describe(df_rs))

df_rs
dftab2
dftab2 <- dftab2[-c(1,6,8,9),]
dftab2 <- dftab2[c(5,1,2,3,4),]
dftab2


rownames(dftab2) <- c("Echo Chamber Index", "Gini","Reciprocity","Degree","Clustering \nCoefficient (sqrt)")

dftab2 <- subset(dftab2, select=c(3,4,5,8,9,11))

dftab2


ecicor <- as.data.frame(cor(df_rs[,-c(1,6,8,9)], df_rs$EC_Index))

dftab2<- subset(dftab2, select=-7)
dftab2
dftab2$ecicor <- ecicor[c(5,1,2,3,4),1]

colnames(dftab2) <- c("Mean", "SD", "Median", "Min", "Max", "Skew", "ECI Correlation")



cor.test(df_rs$Gini, df_rs$EC_Index) #***
cor.test(df_rs$Reciprocity, df_rs$EC_Index) #***
cor.test(df_rs$Degree, df_rs$EC_Index) #***
cor.test(df_rs$Cluster_sq, df_rs$EC_Index) #***

kable(dftab2, booktabs=T,linesep="", format="latex", caption="Index and Rescaled Indicators, Descriptive Statistics", digits=3) %>%
kable_styling(position="center", full_width = F) %>% save_kable("TableDesc2v2.tex") 
```


# Figure 4
```{r}
df_rs3 <- df_rs
df_rs3$Ideology <- recode(df_rs3$ideology,"L"="Left-Wing","R"="Right-Wing","N"="Neutral","NP"="Non-Political")
colors <-  c("Left-Wing" = "#FC4E07", "Right-Wing" = "#00AFBB", "Neutral" = "#b680a8", "Non-Political" = "grey")

#tiff("ECIbySubandIdeology.tiff", units="in", width=8, height=5, res=300)

ggplot(df_rs3, aes(x = reorder(Subreddit,EC_Index),y = EC_Index, fill = Ideology)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = colors) +
  labs(title = "Echo Chamber Index by Subreddit and Ideology",
       x = "Subreddit",
       y = "Echo Chamber Index") + theme_bw() +
 theme(axis.text.x = element_text(angle = 45, hjust = 1),plot.title = element_text(hjust=0.5))
#dev.off()

```

## Figure 5
```{r}

#tiff("ECIDistribution.tiff", units="in", width=8, height=5, res=300)
ggplot(df_rs, aes(EC_Index)) + geom_histogram(aes(y=after_stat(density)), binwidth = density(df_rs$EC_Index)$bw,  alpha=1, fill="#4c72b0") + geom_density(fill="lightblue", alpha=0.6, color="darkblue") + theme_bw() + ggtitle("Echo Chamber Index Distribution") +  theme(plot.title = element_text(hjust = 0.5)) + ylab("Density") + xlab("Echo Chamber Index")
#dev.off()

```

## Size Correlation Table (Table 5)
```{r}
# Size Correlation

df_sizecor <- df_rs

df_sizecor$ClusteringCoeff <- unlist(cluster)
df_sizecor$ClusteringCoeff <- as.numeric(RS(df_sizecor$ClusteringCoeff))

ind <- c("Reciprocity", "Gini", "ClusteringCoeff","Cluster_sq", "Degree", "EC_Index")

est <- list()
pval<- list()
varname <- list()
for (var in ind) {
  test_result <- cor.test(df_sizecor$Size, df_sizecor[[var]], method = "pearson")
  est <- append(est, test_result$estimate)
  varname <- append(varname, var)
  pval <- append(pval, test_result$p.value)
}


sizecors <- data.frame(Variable = unlist(varname), Correlation = unlist(est), P.value= unlist(pval))

colnames(sizecors) <- c("Variable","Correlation w.r.t Size", "P-value")

kable(sizecors, booktabs=T,linesep="", format="latex", digits=3) %>%
kable_styling(position="center")# %>% save_kable("SizeCorrelationTable.tex")
```


# Hypothesis Testing 

## H1 and Table 2
```{r}
df_rs$EC_Index <- as.numeric(df_rs$EC_Index)

#political and non-political
df_P <- df_rs[df_rs$type=="P",]
df_NP <- df_rs[df_rs$type=="NP",]


result <- t.test(EC_Index ~ type, data = df_rs)
dfttesttab <- data.frame(
  statistic = result$statistic,
  p_value = result$p.value,
  ci_low = result$conf.int[1],
  ci_high= result$conf.int[2]
)

# non-parametric test 

wilcox.test(df_P$EC_Index, df_NP$EC_Index)

# check that variances are similaar
var(df_NP$EC_Index)
var(df_P$EC_Index)

# t-test result table
kable(dfttesttab , caption = "T-test Results", booktabs = TRUE, format="latex", linesep="") %>% 
kable_styling(position = "center")# %>% save_kable("TTestTab.tex")
```

### Figure 6
```{r}
#tiff("Boxplot1.tiff", units="in", width=8, height=5, res=300)

ggboxplot(df_rs, x = "type", y = "EC_Index",
          ylab = "EC Index", xlab = "Type", color="type", palette= c("#FC4E07", "darkgrey"), add="jitter") + theme_bw() + xlab("Type of Community") + ylab("Echo Chamber Index") + ggtitle("Box and whisker Plot, Echo Chamber Index by Type")  + theme(legend.position="none", plot.title = element_text(hjust=0.5)) + scale_x_discrete(labels=c("P"="Political", "NP"="Non-Political"))

#dev.off()
```

### Homogeneity of Variance test
```{r}
car::leveneTest(EC_Index ~ factor(type), df_rs)
```

## H2 

## Anova, Tukey Test and Table 3.
```{r}
df_rs$Ideology <- recode(df_rs$ideology,"L"="Left-Wing","R"="Right-Wing","N"="Neutral","NP"="Non-Political")

anov1 <- aov(EC_Index ~ Ideology, data=df_rs)
anov1 %>% summary()

tukey <- TukeyHSD(anov1)
tukey <- tidy(tukey)
tukey <- tukey[,-c(1,3)]
kable(tukey,
booktabs=T,col.names = c("Comparison",
                           "Estimate",
                           "C.I. Low",
                           "C.I. High",
                         "Adjusted p-value"),linesep="", format="latex", caption="Tukey HSD test", digits=3) %>%
kable_styling(position="center") #%>% save_kable("TukeyTable.tex")
```

# Table 4
```{r}
pw_res <- pairwise.t.test(df_rs$EC_Index, df_rs$Ideology, p.adjust.method = "none")
pw_pval<- data.frame(pw_res$p.value)


kable(pw_pval,
booktabs=T,linesep="", format="latex", caption="Pairwise t-test p-values, non-adjusted", digits=3) %>%
kable_styling(position="center") #%>% save_kable("PwPvalTable.tex")


```

## Figure 7
```{r}
#tiff("Boxplot2.tiff", units="in", width=8, height=5, res=300)

bp2colors <- c("#FC4E07","#00AFBB","#b680a8","darkgrey")
ggboxplot(df_rs, x = "Ideology", y = "EC_Index",
          ylab = "EC Index", xlab = "Type", color="Ideology", add="jitter",palette=bp2colors) + theme_bw() + xlab("Community Ideology") + ylab("Echo Chamber Index") + ggtitle("Box and Whiskers Plot, Echo Chamber Index by Ideology")  + theme(legend.position="none", plot.title = element_text(hjust=0.5)) + scale_x_discrete(labels=c("L"="Left-Wing","R"="Right-Wing","N"="Neutral" ,"NP"="Non-Political"))

#dev.off()
```

# PCA
```{r}
dfpc <- df_rs

# Perform PCA analysis
pcafit <- prcomp(dfpc[,2:6])

# Principal components table
PC_table <- data.frame(
PC1=round(pcafit$rotation[,"PC1"],3),
PC2=round(pcafit$rotation[,"PC2"],3))

# Principal components table latex

PC_table
kable(PC_table,
booktabs=T,linesep="", format="latex", digits=3) %>%
kable_styling(position="center") %>% save_kable("PCTable.tex") 

```

## PCA weighted index
```{r}
# Extract the PCA weights (loadings) for each variable
pca_w <- data.frame(pcafit$rotation)

pca_w[1]
pc1_w <- pca_w[1]

# normalise weights to add up to 1
normaliser <- 1/ (sum(pc1_w))

pc1_nw <- (pc1_w*normaliser)

# check that they sum up to one
sum(pc1_nw)



# Calculate the index using PCA weights and scores
dfpc$EC_Index_PC <- ((dfpc$Gini*pc1_nw[1,1]) + (dfpc$Reciprocity*pc1_nw[2,1]) + (dfpc$Degree*pc1_nw[3,1]) + (dfpc$Cluster_sq*pc1_nw[4,1])+(dfpc$Size*pc1_nw[5,1]))


# ggpairs with all indicators and ECIs
ggpairs(dfpc, columns=c(7,11))
g3 <-  ggpairs(dfpc, columns = c(2,3,4,5,7,11), lower = list(continuous = wrap(lowerFn, method = "loess",method2="lm"))) + theme_bw() + 
  theme(strip.text.y = element_text(size = 8))
g3

# Normalised weights (footnote 4)

pc1_nwtp <- transpose(pc1_nw)
colnames(pc1_nwtp) <- rownames(pc1_nw)
pc1_nwtp 
rownames(pc1_nwtp) <- "Normalised Weight"

print(pc1_nwtp) # normalised weights

kable(pc1_nwtp, booktabs=T,linesep="", format="latex") %>%
kable_styling(position="center", full_width = F)# %>% save_kable("Normweights.tex") 

```

# Figure 8 (Scree Plot)
```{r}
pca <- pcafit
# Extract eigenvalues

pca$sdev^2/sum(pca$sdev^2)


screeplot(pcafit, type="line")

x <-summary(pcafit)

yplot <- summary(pcafit)$importance[2,]

xplot <- c("PC1","PC2","PC3","PC4","PC5")

dfplot <- data.frame(PC=xplot,Prop_var = yplot)

#tiff("Screeplot.tiff", units="in", width=8, height=5, res=300)

ggplot(dfplot, aes(y=Prop_var, x=PC, group=1)) + geom_point( col="#002147") + xlab("Principal Component") + ylab("Proportion of Variance Explained") + geom_line(linewidth=0.8, col="#002147") + theme_bw() + ylim(0,0.8)+ ggtitle("PCA Scree Plot") + theme(plot.title = element_text(hjust=0.5))

#dev.off()


```


## Appendix Figures


# Figure B.1

```{r}
df_ind$Cluster <- unlist(cluster)

pd3 <- ggplot(df_ind, aes(x = Cluster, fill = "Clustering Coefficient")) +
  geom_density(alpha = 0.5, fill="darkgrey") + xlab("Clustering Coefficient") + ylab("Density") + theme_bw()

df_ind$Cluster <- unlist(cluster)
pd4<- ggplot(df_ind) + geom_density(aes(x = Cluster_sq, fill = "Square root \nof Clustering \nCoefficient"), alpha = 0.5, fill="lightgrey") +
  labs(fill = "Variable") + xlab("Square Root of Clustering Coefficient") + ylab("Density") +
  theme_bw()

#tiff("ClusteringCoefficientTransformation.tiff", units="in", width=8, height=5, res=300)

gridExtra::grid.arrange(pd3,pd4, ncol=1, top="Clustering Coefficient Square Root Transformation")

#dev.off()
```
# Figure B.2

```{r}
pd1 <- ggplot(df_ind, aes(x = Degree, fill = "Degree Centrality")) +
  geom_density(alpha = 0.5, fill="darkgrey") + xlab("Degree Centrality") + ylab("Density") + theme_bw()
pd1

df_ind$Degree_sq <- sqrt(df_ind$Degree)

pd2<- ggplot(df_ind) + geom_density(aes(x = Degree_sq, fill = "Square root of Degree Centrality"), alpha = 0.5, fill="lightgrey") +
  labs(fill = "Variable") + xlab("Square Root of Degree Centrality") + ylab("Density") +
  theme_bw()

#tiff("DegreeCentralityTransformation.tiff", units="in", width=8, height=5, res=300)

gridExtra::grid.arrange(pd1, pd2, top="Degree Centrality Transformation")

#dev.off()

df_ind <- subset(df_ind, select=-c(Degree_sq))
```


## Distribution Plots

### Gini coefficient Distribution

```{r}
p1 <- ggplot(df_ind, aes(x=Gini)) + 
  geom_histogram(binwidth=0.08, color="#FFFFFF", fill="#4c72b0") +
  labs(title="Authorship Gini Distribution" ,y="Count") + xlab("Gini") +
  geom_vline(xintercept = mean(df_ind$Gini), color="#002147", linetype="dashed", linewidth=0.8)+
  annotate("text", x=(mean(df_ind$Gini)-0.1), y=16, label=paste("Mean =", round(mean(df_ind$Gini),3)), 
           color="#002147", size=2.5, vjust=1, hjust=0) + 
    geom_vline(xintercept = median(df_ind$Gini), color="blue", linetype="dashed", linewidth=0.8)+
  annotate("text", x=(median(df_ind$Gini)+0.005), y=16, label=paste("Median =", round(median(df_ind$Gini),3)), 
           color="blue", size=2.5, vjust=1, hjust=0) +
  theme_bw() +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold"),
        plot.title=element_text(size=10,face="bold", hjust=0.5),
        axis.line=element_line(size=0.5, color="black"),
        axis.ticks=element_line(size=0.5, color="black"))

p1

```

### Reciprocity Distribution

```{r}
p2<- ggplot(df_ind, aes(x=Reciprocity)) + 
  geom_histogram(binwidth=0.09, color="#FFFFFF", fill="#4c72b0") +
  labs(title="Reciprocity Distribution" ,y="Count") + xlab("Reciprocity") +
  geom_vline(xintercept = mean(df_ind$Reciprocity), color="#002147", linetype="dashed", linewidth=0.8)+
  annotate("text", x=(mean(df_ind$Reciprocity)-0.12), y=11, label=paste("Mean =", round(mean(df_ind$Reciprocity),3)), 
           color="#002147", size=2.5, vjust=1, hjust=0) + 
    geom_vline(xintercept = median(df_ind$Reciprocity), color="blue", linetype="dashed", linewidth=0.8)+
  annotate("text", x=(median(df_ind$Reciprocity)+ 0.01), y=11, label=paste("Median =", round(median(df_ind$Reciprocity),3)), 
           color="blue", size=2.5, vjust=1, hjust=0) + 
  theme_bw() +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold"),
        plot.title=element_text(size=10,face="bold", hjust=0.5),
        axis.line=element_line(size=0.5, color="black"),
        axis.ticks=element_line(size=0.5, color="black"))
```

### Degree Centrality Distribution

```{r}
p3 <- ggplot(df_ind, aes(x=Degree)) + geom_histogram(binwidth=3.55, color="#FFFFFF", fill="#4c72b0") +  labs(title="Degree Centrality Distribution", y="Count") + xlab("Degree Centrality") +  geom_vline(xintercept = mean(df_ind$Degree), color="#002147", linetype="dashed", linewidth=0.8)+
  annotate("text", x=(mean(df_ind$Degree)+0.33), y=11, label=paste("Mean =", round(mean(df_ind$Degree),3)), 
           color="#002147", size=2.5, vjust=1, hjust=0) + 
    geom_vline(xintercept = median(df_ind$Degree), color="blue", linetype="dashed", linewidth=0.8) +  annotate("text", x=(median(df_ind$Degree)-4.4), y=11, label=paste("Median =", round(median(df_ind$Degree),3)), 
           color="blue", size=2.5, vjust=1, hjust=0) +
    theme_bw() +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold"),
        plot.title=element_text(size=10,face="bold", hjust=0.5),
        axis.line=element_line(size=0.5, color="black"),
        axis.ticks=element_line(size=0.5, color="black"))


```


### Clustering coefficient distribution

```{r}
p4 <- ggplot(df_ind, aes(x=Cluster_sq)) + geom_histogram(binwidth=0.08, color="#FFFFFF", fill="#4c72b0") + labs(title="Clustering Coefficient Distribution" ,y="Count") + xlab("Square root of Clustering")+  geom_vline(xintercept = mean(df_ind$Cluster_sq), color="#002147", linetype="dashed", linewidth=0.8) +            annotate("text", x=(mean(df_ind$Cluster_sq)+0.01), y=15.5, label=paste("Median =", round(median(df_ind$Cluster_sq),3)), 
           color="blue", size=2.5, vjust=1, hjust=0) + geom_vline(xintercept = median(df_ind$Cluster_sq), color="blue", linetype="dashed", linewidth=0.8) +  annotate("text", x=(median(df_ind$Cluster_sq)-0.09), y=15.5, label=paste("Mean =", round(mean(df_ind$Cluster_sq),3)), 
           color="#002147", size=2.5, vjust=1, hjust=0) +
  theme_bw() +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold"),
        plot.title=element_text(size=10,face="bold", hjust=0.5),
        axis.line=element_line(size=0.5, color="black"),
        axis.ticks=element_line(size=0.5, color="black"))

```

```{r}
#tiff("IndDistPlot.tiff", units="in", width=8, height=5, res=300)

title1=text_grob("Indicators Distributions", size = 13, face = "bold") 
gridExtra::grid.arrange(p1,p2, p3, p4, top=title1)

#dev.off()
```

# Figure B.2
```{r}
df_ft <- df_rs
df_ft$EC_Index_PC <- dfpc$EC_Index_PC
df_ft$Type <- recode(df_ft$type, "P"="Political", "NP"="Non-Political")
rownames(df_ft) <- df_ft$Subreddit
df_ft <- subset(df_ft, select=-c(Subreddit, ideology, type))
df_ft
kable(df_ft, booktabs=T,linesep="", format="latex", digits=3, caption="Total Results, by Subreddit") %>%
kable_styling(position="center", full_width = F) #%>% save_kable("TotalResultsTable.tex")

```

